Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-18 proposal/mprop.tex
Fix bug

Having reviewed the literature on state of the art approaches to what features
are most important when composing a high quality ticket, our work will
build on top of these methods and will try to improve the validity of the
results through statistical analysis. In the following subsections 
(\ref{experimental_design}, \ref{variables_tested} \ref{contributions}) we will
discuss how the experiment was designed, what variables were chosen
as dependent and independent as well as what contributions our study will bring.

>>>>

Having reviewed the literature on state of the art approaches to what features
are most important when composing a high quality ticket, our work will
build on top of these methods and will try to improve the validity of the
results through statistical analysis. In the following subsections 
(\ref{experimental_design}, \ref{variables_tested}, \ref{contributions}) we will
discuss how the experiment was designed, what variables were chosen
as dependent and independent as well as what contributions our study will bring.
